Simple and robust inference of connectomes using partial correlation coefficients

### 2014-06-11 article.tex
save bibliography place
acknowledge dysco and pascal
wording + ref in metrics section

% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
datasets are time series of size $n=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
to inferred have around 15000 arcs or a density of $0.15\%$ and are similar to those
used to rank challenge participants.

Note that our parameter tuning was mainly done on the \textit{normal-1} dataset
and partly on \textit{normal-4} dataset, therefore it may justify why these
networks are better retrieved despite the fact that some might be simpler to
infer.

% Metrics : ROC AUC and AUPRC
The network inference task can be viewed as a binary classification task
where one have to correctly classified the presence or the absence of edges
of the graph. The connectivity score matrix
$\hat{y}_{i,j} \in \mathcal{R}$ inferred by a modeling technique
can be thresholded by a value $\tau \in \mathcal{R}$ to evaluate its performance.
Given the ground true network $y_{i,j} \in \left\{0, 1\right\}$, we first define the notion of
true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
false positive $fp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} \geq \tau)$.
Those four numbers formed the confusion matrix.

We assess the accuracy of the network inference using the area under
the ROC curve (ROC AUC) obtained by varying the threshold
$\tau$ of the true positive rate $tpr(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
as a function of the false positive rate
$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$. In section (TODO ref),
we also compare the same methods with the area under the precision-recall
curve (AUPRC), an information retrieval metrics, obtained by varying the threshold
$\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$
as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$.
Since there is no self connection (neuron connected to itself), we set
the diagonal elements of $\hat{y}_{i,j}$ to the minimum.

@@

\paragraph{Acknowledgements.} A. Joly and G. Louppe are research fellows of
the FNRS, Belgium.  A. Sutera is supported by
a F.R.I.A. scholarship.

@@

\bibliography{references}

>>>>

% Datasets
To assess our method, we have used four datasets provided by the organizer
of the Connectomics challenge : normal-1, normal-2, normal-3, normal-4. Those
datasets are time series of size $n=179500$ of image calcium from simulated
neuronal network \cite{stetter2012model} with $p=1000$ neurons. The networks
to inferred have around 15000 arcs or a density of $0.15\%$ and are similar to those
used to rank challenge participants. Note that our parameter tuning was mainly
done on the \textit{normal-1} dataset and partly on \textit{normal-4} dataset,
therefore it may justify why these networks are better retrieved despite the
fact that some might be simpler to infer.

% Metrics : ROC AUC and AUPRC
The network inference task can be viewed as a binary classification task
where one has to correctly classified the presence or the absence of edges
of the graph. Given the ground true network $y_{i,j} \in \left\{0, 1\right\}$,
the connectivity score matrix $\hat{y}_{i,j} \in \mathcal{R}$
and threshold value $\tau$, we first define the notion of
true positive $tp(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} \geq \tau)$,
true negative $tn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 0, \hat{y}_{i,j} < \tau)$,
false negative $fn(\tau) = \sum_{i=1}^p \sum_{j=1}^p I(y_{i,j} = 1, \hat{y}_{i,j} < \tau)$ and
false positive $fp(\tau) = n - tp(\tau) - tn(\tau) -fn(\tau)$.

We assess the accuracy of the network inference using the area under
the ROC curve (ROC AUC) obtained by varying the threshold
$\tau$ of the true positive rate $tpr(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
as a function of the false positive rate
$fpr(\tau) = \frac{tn(\tau)}{tn(\tau) + fp(\tau)}$.  As suggested in
\cite{schrynemackers2013protocols},
we also compare the same methods with the area under the precision-recall
curve (AUPRC) obtained by varying the threshold
$\tau$ of the precision $P(\tau) = \frac{tp(\tau)}{tp(\tau) + fp(\tau)}$
as a function of the recall $R(\tau) = \frac{tp(\tau)}{tp(\tau) + fn(\tau)}$
in section (todo ref).
Since  there is no self connection (neuron connected to itself), we set
the diagonal elements of $\hat{y}_{i,j}$ to the minimum prior evaluation.

@@

\paragraph{Acknowledgements.} A. Joly and G. Louppe are research fellows of
the FNRS, Belgium.  A. Sutera is  is recipient of
a F.R.I.A. fellowship of F.R.S.-FNRS, Belgium.
This work is supported by PASCAL2 and the IUAP DYSCO, initiated by the
Belgian State, Science Policy Office.

@@

\newpage
\clearpage

% We allow the bibliography to be added on top of the 6 pages.
% Supplementary material may be added in the form or a URL pointed to from
% the paper.
\bibliography{references}
